### 2013-12-29 image_proc_methods.tex
added ref to new model fig; need updates to text from Zach

WHAT GOES HERE?

Although, segmentations were performed along the sagittal plane, label map
intersections in the axial and coronal views were used during active creation
of the sagittal segmentation to further improve segmentation accuracy.  This
was done by using the resampled image stack, B-mode for capsule and ARFI for
CG, as the background in the sagittal plane, and the original image stack as
background in the axial and coronal planes. All three orthogonal views were set
to the label map assigned to the resampled volume. The B-mode derived capsule
was segmented and modeled before the central gland. Parameters used for 3D
model rendering were identical to those used in table X for MR modeling. The
modeled capsule  helprf guide the CG segmentation by enabling capsule model
intersections in the three orthogonal planes during CG segmentation. The
capsule provided an outer boundary for the CG segmentation. The capsule and CG
models were then measured identically to the MR measurement procedure.

>>>>

ZACH - WHAT GOES HERE?

Although, segmentations were performed along the sagittal plane, label map
intersections in the axial and coronal views were used during active creation
of the sagittal segmentation to further improve segmentation accuracy.  This
was done by using the resampled image stack, B-mode for capsule and ARFI for
CG, as the background in the sagittal plane, and the original image stack as
background in the axial and coronal planes. All three orthogonal views were set
to the label map assigned to the resampled volume. The B-mode derived capsule
was segmented and modeled before the central gland. Parameters used for 3D
model rendering were identical to those used in table X [ZACH] for MR modeling.
The modeled capsule helped guide the CG segmentation by enabling capsule model
intersections in the three orthogonal planes during CG segmentation
(Figure~\ref{fig:arfi_seg}). The capsule provided an outer boundary for the CG
segmentation. The capsule and CG models were then measured identically to the
MR measurement procedure.
